### 2016-01-28 paper/response.tex

\setcounter{table}{2}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{| c | l | c c c |}
  \hline                        
  Category & Parameter & Avian H5N1 & Seasonal H1N1 & Pandemic H1N1 \\
  \hline
  \multirow{3}{*}{Chemokine} & Chemokine Decay Rate & \cellcolor{blue!30}bounded stable & \cellcolor{blue!30}bounded stable & \cellcolor{green!50}stable \\
  & Chemokine Diffusion Rate & \cellcolor{blue!30}bounded stable & \cellcolor{green!50}stable& \cellcolor{green!50}stable \\
  & Chemokine Secretion Rate & \cellcolor{blue!30}bounded stable & \cellcolor{green!50}stable & \cellcolor{green!50}stable \\
  \hline
  \multirow{6}{*}{T Cell} & Circulation Time & \cellcolor{blue!30}bounded stable & \cellcolor{blue!30}bounded stable & \cellcolor{blue!30}bounded stable \\
  & T Cell Kill Rate & \cellcolor{green!50}stable & \cellcolor{blue!30}bounded stable & \cellcolor{blue!30}bounded stable \\
  & T Cell Speed & \cellcolor{green!50}stable & \cellcolor{blue!30}bounded stable & \cellcolor{blue!30}bounded stable \\
  & T Cell Age in Blood& \cellcolor{green!50}stable & \cellcolor{blue!30}bounded stable& \cellcolor{blue!30}bounded stable \\
  & T Cell Age at FOI& \cellcolor{green!50}stable & \cellcolor{blue!30}\textbf{bounded stable$^\dagger$} & \cellcolor{blue!30}bounded stable \\
  & T Cell Production Rate & \cellcolor{blue!30}bounded stable & \cellcolor{blue!30}bounded stable & \cellcolor{blue!30}bounded stable \\
  \hline
  \multirow{3}{*}{Delay} & Apoptosis Time & \cellcolor{green!50}stable & \cellcolor{green!50}stable & \cellcolor{green!50}stable \\
  & Expression Time & \cellcolor{yellow!50}peak change & \cellcolor{yellow!50}\textbf{peak change$^\dagger$} & \cellcolor{yellow!50}peak change \\
  & Incubation Time &  \cellcolor{yellow!50}peak change & \cellcolor{yellow!50}peak change & \cellcolor{yellow!50}peak change \\
  \hline 
  \multirow{4}{*}{Virus} & Viral Response to IgM & \cellcolor{red!40}sensitive & \cellcolor{red!40}\textbf{sensitive$^\dagger$} & \cellcolor{red!40}sensitive \\
  & Infectivity & \cellcolor{red!40}sensitive & \cellcolor{red!40}\textbf{sensitive$^*$} & \cellcolor{red!40}sensitive \\
  & Viral Decay Rate & \cellcolor{red!40}sensitive & \cellcolor{red!40}\textbf{sensitive$^*$} & \cellcolor{red!40}sensitive \\
  & Viral Diffusion Rate & \cellcolor{red!40}sensitive & \cellcolor{red!40}\textbf{sensitive$^*$} & \cellcolor{red!40}sensitive \\
  \hline  
\end{tabular}
\caption{\textbf{Sensitivity Results:} The above parameters were varied over predetermined ranges in isolation, resulting in new model runs for every new value tested (Figs. S3-S5).  The results of the sensitivity analysis were then qualitatively evaluated for each individual parameter.  A model run's behavior was determined by examining the height of the peak of the infection at day 5 post-infection and the number of infected cells at day 10 post-infection.  Each combination of influenza strain and free parameter was classified as belonging to one of four categories.  Parameters were classified as \textbf{stable} if all runs follow the same behavior, \textbf{bounded stable} if intermediate parameter adjustments did not affect the model's behavior, even if the more extreme adjustments did, \textbf{peak change} if the peak of the infection differs but the result at day 10 is the same, and \textbf{sensitive} if any level of change in the parameter affects the resulting model behavior.  \new{PRCC analysis was also performed for the sH1N1 strain over these parameters (Figs. S6-S8).  Bold text in the seasonal column denotes significant Spearman rank correlation ($P < 0.01$) over the time period where the parameter was active. $\dagger$ indicates a maximum \textit{absolute} Spearman's $\rho$ of less than 0.5.  $*$ indicates a maximum \textit{absolute} Spearman's $\rho$ of over 0.5.}}
\label{tab:sensitivity}
\end{center}
\end{table}

\end{displayquote}
\end{response}
